\begin{rubric}{Employment History}

%   % \twentyitem{<dates>}{<title>}{<location>}{<description>}
%   \twentyitem{2021}{Lupo S.A. -- Jan/2021-May/2021}{Developer}{Wrote software to automate Technical Reports, while working at WJB Engenharia (wjbsegurançadotrabalho.com.br/), as a Contractor firm to Lupo S.A.. We performed the Safety Analysis and Inventory of all the machinery from the company.}
%   \twentyitem{2021}{FlowFinance S.C.- Jun/2021-July/2021}{Developer}{I developed an application, single-handily, to perform the Ledger and Clarence of billing data coming from BIORC, in CSV format. The technology used was Clojure.}
%   \twentyitem{2021/2022}{University of São Paulo - Sep/2021-Mar/2022}{Researcher}{Modeling Traffic Flow, with Julia and Python - numerical solution to Partial Differential Equations (PDEs).Modeling Traffic Flow, with Julia and Python - numerical solution to Partial Differential Equations (PDEs).
% }
% \twentyitem{2021/2022}{Café do Bem (NPO) - Aug/2021-Current}{Volunteer (Free time)}{I created the website \href{https://cafe-do-bem.company.site/}{https://cafe-do-bem.company.site/}, which is a platform to sell coffee. The mission of this Non-profit Organization is to revert all monetary gain, back to the coffee community (housing, food and basic education, as well as specialization courses).
% }

% \twentyitem{2022/2023}{FACTI - Dez/2022-Aug/2023}{Developer}{
% Working on an application to facilitate the accountability of projects, which have been funded by the government. The technologies used are Clojure, Vanilla JavaScript, Angular, JQuery, Express.js, Bootstrap and Material UI.
% }


% \entry*[2014 -- $\cdots\cdot$]%
% 	\textbf{Community Witch,} Village of Frying Pans.
%
% Blank lines result in extra space!
%
\entry*[2023/Jan -- 2023/Aug]%
\textbf{FACTI} Campinas, São Paulo (Hybrid)
\par Created a full stack application to automate the accounting of projects funded by the government. The technologies used were Clojure, Vanilla JavaScript, Angular, JQuery, Express.js, Bootstrap and Material UI.

\entry*[2021/Jun - 2022/Dec]
\textbf{Café do Bem (NPO)} Franca, São Paulo (Remote)
\par I created the full stack website \href{https://cafe-do-bem.company.site/}{https://cafe-do-bem.company.site/}, which is a platform to sell coffee. The mission of this Non-profit Organization is to revert all monetary gain, back to the coffee community (housing, food and basic education, as well as specialization courses).

\entry*[2021/Sep - 2022/Dec]
\textbf{University of São Paulo} Lorena, São Paulo (Remote)
\par Modeled Traffic Flow, with Julia and Python - numerical solution to Partial Differential Equations (PDEs) - as a Researcher.

\entry*[2021/Agu - 2021/Sep]
\textbf{FlowFinance} Santa Catarina, Rio Grande do Sul (Remote)
\par I developed an application to perform the Ledger and Clarence of billing data coming from BIORC, in CSV format. The technology used was Clojure. The end-product was an API system to handle common manual tasks.

\entry*[2021/Jan - 2021/May]
\textbf{Lupo S.A.} Araraquara, São Paulo (Hybrid)
\par Wrote software to automate Technical Reports, while working at WJB Engenharia (wjbsegurançadotrabalho.com.br/), as a Contractor firm to Lupo S.A.. We performed the Safety Analysis and Inventory of all the machinery from the company.


\end{rubric}
