\begin{rubric}{Miscellaneous Experience}
\subrubric{Eletronic Publications}
\entry*[2021]
{\href{https://github.com/BuddhiLW/CloshBashika}{\color{blue!50!violet}
    Industry (Lupo S.A.) - Automate technical reports with Clojure/LaTeX.}}
\entry*[2021]
\href{https://github.com/BuddhiLW/commons-csv-clj}{\color{blue!50!violet} FlowFinance - Clojure, library for CSV data-manipulation}
\entry*[2020]
\href{https://github.com/BuddhiLW/EEL_EstatMultiVarRN}{\color{blue!50!violet} Machine Learning, with R.}
\entry*[2020]{\href{https://github.com/BuddhiLW/MC-LaTeX/tree/master/LabEELw/LabEELw/MaterialMC/Livro_PT1}{\color{blue!50!violet}Introduction
      to \LaTeX, P1.}}
\entry*[2020]{\href{https://github.com/BuddhiLW/MC-LaTeX/tree/master/LabEELw/LabEELw/MaterialMC/Livro_PT2}{\color{blue!50!violet}      Essential Commands in \LaTeX, P2.}}
\entry*[2020]{\href{https://github.com/BuddhiLW/MC-LaTeX/tree/master/LabEELw/LabEELw/MaterialMC/Livro_PT3}{\color{blue!50!violet}Bibliographical      References, Citations and Beamer Presentations, P3.}}
\entry*[2020]{\href{https://www.youtube.com/watch?v=spYCKElN-v0&list=PLweBgessvalf9eGUknfHQZ6_q2Nz7t8df}{\color{blue!50!violet}  A Minicourse on \LaTeX{}} - Material available on YouTube (Portuguese).}
  % \twentyitemshort{2020}{\href{https://www.youtube.com/watch?v=spYCKElN-v0&list=PLweBgessvalf9eGUknfHQZ6_q2Nz7t8df}{\color{blue!50!violet}
  %   A Minicourse on \LaTeX{}} - Material available on YouTube (Portuguese).}

\subrubric{Certification}

\entry*[2022]\textbf{\href{https://buddhilw.github.io/bug-free-fiesta/}{Getting Started with Go (UCLA Irvine):}} Basic syntax and Data Structure.
\entry*[2022]\textbf{\href{https://buddhilw.github.io/bug-free-fiesta/}{Functions, Methods and Interfaces (UCLA Irvine):}} Object Orientation in Go.
\entry*[2022]\textbf{\href{https://buddhilw.github.io/bug-free-fiesta/}{Concurrency in Go (UCLA Irvine):}} Advanced features in Go.

\entry*[2022]\textbf{\href{https://buddhilw.github.io/bug-free-fiesta/}{Introduction to Back-End Development (Meta):}} Agile, TDD etc.; the infrastructure of the web, HTTP, CTP and other Protocols..
\entry*[2022]\textbf{\href{https://buddhilw.github.io/bug-free-fiesta/}{Version Control (Meta):}} Practices with Git and Github.
\entry*[2022]\textbf{\href{https://buddhilw.github.io/bug-free-fiesta/}{Programming in Python (Meta):}} Syntax, and Object Orientation.

\entry*[2022]\textbf{\href{https://buddhilw.github.io/bug-free-fiesta/}{EF SET Score - C2}} English test - European Standards - 78/100 points

% \entry*[2014] \textbf{Certified XYZ Practioner}. Awarded by X Insitute.
% \entry*[2006] \textbf{Certified Level 3 in ABC}. Awarded by ABC.

\end{rubric}
